---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# songify

<!-- badges: start -->
[![R-CMD-check](https://github.com/kbacigalupi/songify/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kbacigalupi/songify/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of songify is to allow users to generate a recommended song or playlist with inputs that they set.

## Installation

You can install the development version of songify from [GitHub](https://github.com/) with:

```{r}
install.packages("devtools")
devtools::install_github("kbacigalupi/songify")
library(songify)
```

## Using Songify

Use the `rec_song()` function with a variety of potential inputs to get a single song recommendation. 

```{r, eval = FALSE}
rec_song("pop", instrumentalness = 1)
```

Use the `rec_playlist()` function with a variety of potential inputs to get a full playlist recommendation. 

```{r, eval = FALSE}
rec_playlist("hip hop", nsongs = 10)
```

## Data Set 
Songify also includes a data set of Taylor Swift Songs with a variety of measures of song type.

```{r, eval = FALSE}
songify::song_bank
```


