---
title: "Using the songify package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the songify package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(spotifyr)

credentials <- tryCatch(expr = {
    list(token = spotifyr::get_spotify_access_token(), found = TRUE)
  },
  error = function(e) {
    list(token = NA_character_, found = FALSE)
  }
)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = credentials$found
)
```

```{r eval=!credentials$found}
message("No spotify credentials found. Subsequent code chunks will not be evaluated.")
```

## Generating a recommended song

The main function of the songify package is to generate a song or a playlist given user inputs including genre, mode, energy, valence, danceability, and instrumentalness. Let's see how we can accomplish this. First, load the `songify` package.

```{r setup}
library(songify)
```

Then, use the `rec_song()` function to generate a song recommendation. We'll retrieve information about a pop song, so we'll set the `genre` argument as 'pop' and the `energy` will be set to 0.8. For the parameters `energy`, `mode`, `valence`, `danceability`, `instrumentalness` can be enters on a sliding scale from 0.0-1.0. You can be as specific as you want and go to many decimal places.

```{r}
a_song <- rec_song("pop", energy = 0.8)
```

The objects returned by `rec_song()` are of the S3 class 'song'

To generate the playlist, use the `rec_playlist()` function. We'll retrieve a playlist using an argument for `genre` and `nsongs` which will be the number of songs you want in your playlist. We will retrieve a playlist for 5 songs.

```{r}
a_playlist <- rec_playlist("pop", 5)
```

## Song Bank Data

The `songify` package also comes with a built in data set with all of the songs by Taylor Swift (as of April 2024) 

```{r}
songify::song_bank
```


